# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
I download the file from: https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip,
unzip it and then read it with R:
```{r}
data<-read.csv("activity.csv")
dateDownload<-date()
```

## What is mean total number of steps taken per day?
In the barplot we can see the total number of steps per day.
```{r}
barplot(tapply(data$steps, data$date, sum,na.rm=TRUE), las=2)
stepsPerDay<-tapply(data$steps, data$date, sum,na.rm=TRUE)
summary(stepsPerDay)[4]
summary(stepsPerDay)[3]
```
The mean of steps per day is 9354 and the median is 10400.

## What is the average daily activity pattern?

The time series plot shows the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis):
```{r}
plot(tapply(data$steps, data$interval, mean,na.rm=TRUE), type = "l")
stepsPerInterval<-tapply(data$steps, data$interval, mean,na.rm=TRUE)
which.max(stepsPerInterval)
stepsPerInterval[104]
```

The 5-minute interval, on average across all the days in the dataset, that contains the maximum number of steps is 835.
With 206.1698 steps.


## Imputing missing values
There are 2304 NAs on this dataset.
By inspecting it a little I saw that all NAs correspond to the whole intervals of 8 complete days (2012-10-01,2012-10-08,2012-11-01,2012-11-04,2012-11-09,2012-11-10,2012-11-14 and 2012-11-30).
I prefer to work without these days, with the reduced dataset of the real mesures that were taken.
```{r}
sum(is.na(data))
newData<-data
which(is.na(newData))
newData<-na.omit(newData)
```
I compared this reduced dateset with the one used in the first question:
```{r}
barplot(tapply(newData$steps, newData$date, sum), las=2)
newStepsPerDay<-tapply(newData$steps, newData$date, sum)
summary(newStepsPerDay)[4]
summary(newStepsPerDay)[3]
```
As expected, the mean of the total steps per day is higher in the reduced dataset as well as the median.

## Are there differences in activity patterns between weekdays and weekends?
From this graph we can see that the mean of steps per interval is almost the same in the first 500 intervals, between intervals 500 and 1000 people move a little bit more on weekdays, and for the next intervals (till interval 2000) people are moving more on weekends.
I can said that the patterns are different from weekdays and weekend.
```{r}
library("timeDate")
library("lattice")
newData$day<-ifelse(isWeekday(newData$date),"weekday","weekend")
results<-aggregate(newData$steps, by=list(newData$day,newData$interval),FUN=mean)
names(results)[1]<-"day"
names(results)[2]<-"interval"
names(results)[3]<-"mean"
xyplot(mean~interval|day,results, type="l",layout=(c(1,2)))
```

